\chapter{Testing}
\textbf{1. Integration Testing:}\\
Technique: Verify the seamless integration of encryption modules, load balancer, GitHub, and
Firebase authentication.\\
Tools: JUnit, TestNG, Postman (for API testing).\\
Test Cases:\\
Verify that data is encrypted using RSA algorithm before storage.\\
Test the integration between Firebase authentication and user access control mechanisms.\\
Confirm that the load balancer efficiently distributes data across multiple nodes.
\\
\\
\textbf{2. Performance Testing:}\\
Technique: Evaluate the system's performance under various conditions, such as load, stress, and
scalability.\\
Tools: Apache JMeter, Gatling.\\
Test Cases:\\
Simulate a high load to ensure the load balancer effectively distributes data without performance
degradation.\\
Test the system's response time during peak usage.
Evaluate the scalability of the system by gradually increasing the load. 
\\
\\
\textbf{3. Security Testing:}\\
Technique: Identify vulnerabilities and ensure the system's resistance against attacks.\\
Tools: OWASP ZAP, Burp Suite.\\
Test Cases:\\
Conduct penetration testing to identify potential security flaws.
Verify the implementation of Firebase authentication for secure user access.\\
Test for encryption and decryption vulnerabilities in the RSA algorithm. 
\\
\\
\textbf{4. Usability Testing:}\\
Technique: Assess the user-friendliness of the system.\\
Tools: UsabilityHub, UserTesting.\\
Test Cases:\\
Evaluate the clarity and effectiveness of user manuals.\\
Validate the ease of use for administrators in managing load balancing through GitHub.
\\
\\
\textbf{5. Compatibility Testing:}\\
Technique: Ensure compatibility with different browsers, devices, and platforms.\\
Tools: BrowserStack, Sauce Labs.\\
Test Cases:\\
Test the system on various web browsers (Chrome, Firefox, Safari).\\
Verify compatibility with different operating systems (Windows, macOS, Linux). 
\\
\\
\textbf{6. Regression Testing: }\\
Technique: Ensure that new updates or features do not negatively impact existing functionalities.\\
Tools: Selenium, TestNG.\\
Test Cases:\\
Confirm that encryption updates do not introduce data corruption.\\
Validate that GitHub integration updates do not disrupt version control. 
\\
\\
\textbf{7. Load Balancer Testing:}\\
Technique: Verify the load balancer's effectiveness in distributing data and optimizing resource
utilization.\\
Tools: Apache Bench, Locust.\\
Test Cases:\\
Evaluate the load balancer's ability to evenly distribute data across multiple cloud storage nodes.\\
Test the load balancer's response to varying levels of incoming data. 
\\
\\
\textbf{8. GitHub Integration Testing:}\\
Technique: Confirm the seamless integration of GitHub repositories for efficient storage
management.\\
Tools: GitLab CI/CD, GitHub Actions.\\
Test Cases:\\
Verify that multiple repositories for a single user are created and managed appropriately.\\
Test version control by updating files in the repositories and confirming changes are reflected. 
\\
\\
\textbf{9. Firebase Authentication Testing:}\\
Technique: Validate the integration and security of Firebase authentication for user access control.\\
Tools: Firebase Emulator Suite, Postman.\\
Test Cases:\\
Test user registration and authentication processes.\\
Verify access controls based on Firebase authentication. 
\\
\\
\textbf{10. Post-Quantum Encryption Testing: }\\
Technique: Assess the effectiveness and compatibility of post-quantum encryption techniques.\\
Tools: Quantum Development Kit (Q#), NIST PQC Standardization Testing.\\
Test Cases:\\
Confirm the proper implementation of post-quantum encryption algorithms.\\
Validate backward compatibility with existing encryption methodologies. 
\\
\\
\textbf{Note:}\\
Test Environment: Create isolated test environments to ensure testing does not impact the production
system.\\
Documentation: Maintain detailed documentation for each test case, including expected results and
actual outcomes.\\
These testing techniques and tools, along with the provided test cases, will help ensure the robustness,
security, and efficiency of the "SecureCloud" system.

